August-ish Manuscript Edits

### 2020-01-29 2019_edits/R/fecundity_analyses/egg_models_2.Rmd
paths changed for reproductive analyses

#Egg Data
eggdat <- read_csv(here("data/repo/seamap_summerandfall2017_crabs.csv"), guess_max = 10000, col_types = cols())
eggdat <- eggdat %>% 
  mutate(Egg_stage = factor(eggdat$Egg_stage),
         molt_stage = factor(molt_stage),
         Estimated_fecundity = ifelse(Estimated_fecundity == "#DIV/0!", NA, Estimated_fecundity),
         Estimated_fecundity = as.numeric(Estimated_fecundity))

#Stations
stat_dat <- read_csv(here("data/repo/2017_allcrabs_onerow_withstationdata.csv"), guess_max = 10000, col_types = cols())
eggdat <- stat_dat %>%  
  select(Unique_ID, Agency, STA_TIME, END_TIME,STA_LON, STA_LAT) %>% 
  right_join(eggdat, by = "Unique_ID")

#Regions and Statzones
# Add the statzone using statzone polygon - use this to make regions consistent between models
szones <- read_sf(here("data/gis_files","NMFS_Fishing_Grids_GOM_2013.shp"), crs = 4326)

>>>>

#Egg Data - one record per egg
eggdat <- read_csv("~/Dropbox/SEAMAP_2019/data/repro/seamap_summerandfall2017_crabs.csv", 
                   guess_max = 10000, col_types = cols())

eggdat <- eggdat %>% 
  mutate(Egg_stage = factor(eggdat$Egg_stage),
         molt_stage = factor(molt_stage),
         Estimated_fecundity = ifelse(Estimated_fecundity == "#DIV/0!", NA, Estimated_fecundity),
         Estimated_fecundity = as.numeric(Estimated_fecundity))

#Stations - one row per crab record
stat_dat <- read_csv("~/Dropbox/SEAMAP_2019/data/repro/2017_allcrabs_onerow_withstationdata.csv", 
                     guess_max = 10000, col_types = cols())
eggdat <- stat_dat %>%  
  select(Unique_ID, Agency, STA_TIME, END_TIME,STA_LON, STA_LAT) %>% 
  right_join(eggdat, by = "Unique_ID")

#Regions and Statzones
# Add the statzone using statzone polygon - use this to make regions consistent between models
szones <- read_sf("~/Dropbox/SEAMAP_2019/data/gis_files/NMFS_Fishing_Grids_GOM_2013.shp", crs = 4326)
